My title

### 2023-10-03 outputs/paper/paper.qmd
Initial data presentation

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

>>>>

```{r}
#| echo: false
#| message: false
#| warning: false

#### Workspace setup ####
library(tidyverse)
library(knitr)

#### Read in the cleaned data ####
data <- read_csv(here::here("outputs/data/cleaned_bicycle_theft.csv"), show_col_types = FALSE)
```

# Introduction

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

data |> group_by(occ_year) |> summarise(total = n()) |> kable()
```

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

data |> ggplot(aes(x=occ_year, fill=location)) +
  geom_bar()

```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

data |> ggplot(aes(x=occ_year, fill=bicycle_status)) +
  geom_bar()
```

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

data |> filter(difference <= 100) |> 
  ggplot(aes(x=occ_year, y=difference, color=occ_month)) +
  geom_point()
```
```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

data |> group_by(occ_month) |> summarise(total = n()) |> kable()

```

\newpage

# References
